---
title: Events
execute: 
  echo: false
  output: asis
  warning: false
---

```{r workspace}
#| include: false
library(htmltools)
library(glue)

general_card_div <- function(..., lg = 3, md = 2, sm = 2, xs = 1) {
  class_info <- 
    paste(
      "card",       # card class
      # about card
      "rounded-3",  # border-radius = 0.3rem
      "m-2",        # margin all sides: 0.5rem
      # about grid placement
      glue("g-col-lg-{12/lg}"), # when >=1200px use {lg} cols per card (ex. 3 across)
      glue("g-col-md-{12/md}"), # when >= 992px use {md} cols per card (ex. 2 across)
      glue("g-col-sm-{12/sm}"), # when >= 768px use {sm} cols per card (ex. 2 across)
      glue("g-col-{12/xs}")     # when  < 576px use {xs} cols per card (ex. 1 across)
    )
  
  div(
    class = class_info,
    style = "background: #8f4b99;",
    ...
  )
}
```

:::::: {.content-block}

The Social Justice Hackathon will take place at University of Pennsylvania Carey Law School<br>
3501 Sansom St, Philadelphia, PA 19104

## Upcoming Events

::: {.list .grid}
      
```{r info-cards}
#| eval: true
add_info_card <- function(title, body, button_text, button_link) {
  general_card_div(
    div(
      class = "card-body",
      # title
      tags$section(
        class = "card-title text-center",       
        h5(title)
      ),
      # body
      br(),
      p(body),
      br()
    ),
    # button
    div(
      class = "d-flex justify-content-center mb-3",
      #class = "card-footer",
      tags$a(
        class = "btn btn-action btn-primary btn-action-primary justify-content-center",
        button_text,
        href = button_link
      )
    )
  )
}

add_info_card(
  title = "Hack Night \n(Temple)",
  body =
    "Date: March 12, 2026",
  button_text = "Register now",
  button_link = "https://www.eventbrite.com/e/sjhphl-hack-night-prep-for-philadelphia-social-justice-hackathon-tickets-1983381897647"
)

add_info_card(
  title = "Social Justice Hackathon",
  body =
    "Date: March 27-29, 2026",
  button_text = "Register now",
  button_link = "https://www.eventbrite.com/e/1983329295312"
)
```
:::

## Schedule

| Day | Main Activity | Description |
| --- | --- | --- |
| Day 1, Friday, March 27th | Kickoff and Keynote by [Clarence Okoh](https://www.clarenceokoh.com/) | Hackathon Project Pitches by Project Sponsors and Participants; Team Formation and Matching. <br><br> [See our 3 challenge tracks for project suggestions](posts/2026-03-19-challenge-tracks.qmd) |
| Day 2, Saturday, March 28th | Challenge analysis and planning | Hackathon orientation sessions: design thinking, platforms and data available. Solutions design and development |
| Day 3, Sunday, March 29th | Solution development and presentation prep | Project Final Submissions.  Judging.  Closing Ceremony <br><br> The winning project will be advanced to the [Information Architecture Conference](https://www.theiaconference.com/) design hackathon. |

## Speakers

```{r speakers}
library(commonmark)

add_speaker_card <- function(name, img, bio, link = NULL) {
  general_card_div(
    div(
      class = "card-body text-center",
      a(
        img(src = file.path("assets/speakers", img), height = "100px"),
        href = link
      ),
      p(
        class = "text-center mt-3",
        a(name, href = link),
        style = "font-size: 1.2rem;"
      ),
      p(
        class = "text-center person-bio",
        HTML(commonmark::markdown_html(bio))
      )
    ),
    lg = 2, md = 2, sm = 1, xs = 1
  )
}

tagList(
  add_speaker_card(
    name = "Clarence Okoh",
    img = "clarence-okoh.png",
    link = "https://www.clarenceokoh.com/",
    bio = "**Friday Keynote.** Clarence holds over a decade of experience advancing social change through legal and policy advocacy. He is a nationally recognized expert on the role of emerging technologies in producing racial and social inequality through algorithmic racism, mass surveillance, and other privacy and civil rights abuses. He offers a wide breadth of experience: from serving as the first digital justice litigator at the NAACP Legal Defense Fund to leading community-based direct services in his native Alabama."
  ),
  add_speaker_card(
    name = "Jaimie Yakaboski",
    img = "jaimie-yakaboski.jpeg",
    link = "https://www.linkedin.com/in/jaimie-yakaboski/",
    bio = "**Saturday Workshop: Design Thinking & Structured Problem Solving.** Jaimie is a seven year veteran in Digital Product Design and UX with a special interest in systemic design and design within healthcare. They enjoy seeking opportunities to solve complex problems with creative solutions grounded in research and data.\n\nJaimie spent six and a half years with Independence Blue Cross, but now seeks their next opportunity. Jaimie is on the volunteer board running IAC26 and also frequents [Philly CHI](https://www.meetup.com/PhillyCHI/), Philly's local chapter for UX Professionals!"
  )
) |> div(class = "list grid")
```

## Venue

::::: {.grid}

::: {.g-col-12 .g-col-lg-4}
University of Pennsylvania Carey Law School
3501 Sansom St
Philadelphia, PA 19104
:::

::: {.g-col-12 .g-col-lg-8}

<iframe src="https://www.google.com/maps/embed?pb=!1m18!1m12!1m3!1d3058.440700719378!2d-75.19583322341768!3d39.953898583677955!2m3!1f0!2f0!3f0!3m2!1i1024!2i768!4f13.1!3m3!1m2!1s0x89c6c65066c9680d%3A0x9f0ce0d718af648!2sPenn%20Carey%20Law!5e0!3m2!1sen!2sus!4v1769472012279!5m2!1sen!2sus" width="600" height="450" style="border:0;" allowfullscreen="" loading="lazy" referrerpolicy="no-referrer-when-downgrade"></iframe>

:::

:::::

### Directions

See the "Directions & Transit" section on [Penn Carey Law's visiting page](https://www.law.upenn.edu/admissions/visiting/) for directions and parking information.

::::::
