---
title: Events
execute: 
  echo: false
  output: asis
  warning: false
---

```{r workspace}
#| include: false
library(htmltools)
library(shiny) # markdown()
library(glue)

general_card_div <- function(..., lg = 3, md = 2, sm = 2, xs = 1) {
  class_info <- 
    paste(
      "card",       # card class
      # about card
      "rounded-3",  # border-radius = 0.3rem
      "m-2",        # margin all sides: 0.5rem
      # about grid placement
      glue("g-col-lg-{12/lg}"), # when >=1200px use {lg} cols per card (ex. 3 across)
      glue("g-col-md-{12/md}"), # when >= 992px use {md} cols per card (ex. 2 across)
      glue("g-col-sm-{12/sm}"), # when >= 768px use {sm} cols per card (ex. 2 across)
      glue("g-col-{12/xs}")     # when  < 576px use {xs} cols per card (ex. 1 across)
    )
  
  div(
    class = class_info,
    style = "background: #8f4b99;",
    ...
  )
}
```

:::::: {.content-block}

All events will take place at Drexel University Thomas R. Kline School of Law<br>
3320 Market St, Philadelphia, PA 19104

## Upcoming Events

::: {.list .grid}
      
```{r info-cards}
#| eval: true
add_info_card <- function(title, body, button_text, button_link) {
  general_card_div(
    div(
      class = "card-body",
      # title
      tags$section(
        class = "card-title text-center",       
        h5(title)
      ),
      # body
      br(),
      p(body),
      br()
    ),
    # button
    div(
      class = "d-flex justify-content-center mb-3",
      #class = "card-footer",
      tags$a(
        class = "btn btn-action btn-primary btn-action-primary justify-content-center",
        button_text,
        href = button_link
      )
    )
  )
}

add_info_card(
  title = "Social Justice Hackathon", 
  body = 
    "Date: April 5-7, 2024", 
  button_text = "Register now", 
  button_link = "https://www.eventbrite.com/e/philadelphia-social-justice-hackathon-2024-tickets-829209476867"
)
```
:::

## Schedule

| Day | Main Activity | Description |
| --- | --- | --- |
| Day 1, Friday, April 5th | Kickoff and Keynote | Hackathon Project Pitches by Project Sponsors and Participants; Team Formation and Matching. |
| Day 2, Saturday, April 6th | Challenge analysis and planning | Hackathon orientation sessions: design thinking, platforms and data available. Solutions design and development |
| Day 3, Sunday, April 7th | Solution development and presentation prep | Project Final Submissions.  Judging.  Closing Ceremony |

## Venue

::::: {.grid}

::: {.g-col-12 .g-col-lg-4}
Drexel University Thomas R. Kline School of Law  
3320 Market St  
Philadelphia, PA 19104
:::

::: {.g-col-12 .g-col-lg-8}

<iframe src="https://www.google.com/maps/embed?pb=!1m18!1m12!1m3!1d3058.3732790637437!2d-75.19301808771128!3d39.95540627139878!2m3!1f0!2f0!3f0!3m2!1i1024!2i768!4f13.1!3m3!1m2!1s0x89c6c651cc8cb83b%3A0xd207bd894c157129!2sDrexel%20University%20Thomas%20R.%20Kline%20School%20of%20Law!5e0!3m2!1sen!2sus!4v1710446008805!5m2!1sen!2sus" width="100%" height="360" style="border:0;" allowfullscreen="" loading="lazy" referrerpolicy="no-referrer-when-downgrade"></iframe>

:::

:::::

### Directions

See [this Drexel Directions page](https://drexel.edu/law/admissions/tours-info-sessions-events/Directions/) for more.

### Parking

The Drexel Garage is located next to the law school. Proceed to 34th and Market Streets - there is a traffic light there - (you'll also pass the Law School Building on your left before the light). Turn left onto 34th Street - and make an immediate left onto the next street - Ludlow Street. Turn immediately left up to the entrance ramp to the garage on Ludlow Street. Park, note your place number, and pay at the lobby kiosk. Come down the elevator, exit the building and walk right. The law school is immediately to the right of the garage, just past the front of the parking garage.

Metered parking is also available on many of the surrounding streets. The meters accept quarters, dimes and nickels for timed parking.

::::::
